---
title: "hcahps_cah_script"
author: "alyssa furukawa"
date: "2024-02-27"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Required packages are loaded below.

```{r}
#renv::install("alyssafurukawa/FMT2")
#devtools::install_github("alyssafurukawa/FMT2")

library(FMT2)
library(gt)
librarian("reports")

read_simple <- function(file, year=2019){
  hcahps_measures <- c("Composite 1", "Composite 2", "Composite 3", "Composite 5", "Composite 6", "Composite 7", 
                       "Q8", "Q9", "Q 21", "Q 22")
  
  hcahps_frame <- readxl::read_xlsx(paste0(fmt_folder, "Data/MBQIP Data/", file)) %>%
    janitor::clean_names() |> 
     mutate(provider_id= as.numeric(provider_id)) 
  
  return(hcahps_frame)
}

#renv::init()
```

Load the MOU list which will remove CAHs that shouldn't be included in the data. Use the most recent available MOU list and update the file path accordingly. Use the information from the MOU list to manually create a list of CAHs that currently have signed MOUs but should be excluded for specific quarters. Unlike in the other quarterly reports, this needs to be done manually because of the several missing quarters of HCAHPS data. If a CAH has a signed MOU, but not yet for the current period, we need to have a CAH report for them but they aren't included in the aggregated (state/national) totals. The value of "quarter" will also need to be updated with each report.

```{r}
quarter <- "2023Q3"
p7_q <- "2023Q2" 
p6_q <- "2023Q1"
p5_q <- "2022Q4"
p4_q <-  "2022Q3"
p3_q <- "2022Q2" 
p2_q <- "2022Q1"
p1_q <- "2021Q4"

lastQ_data <- "MBQIP Reports/Quarterly Reports/HCAHPS/2023Q2/R/Data/hcahps_2023Q2_2024-01-30.Rdata"
#^^^^^^ manually update for every report ^^^^^^^^^^^^^^^^^


#MOU list
list <- readxl::read_xlsx(paste0(fmt_folder, "MBQIP Reports/CAH List with MOU_FMT 4.15.24.xlsx"), sheet = "CAHs with MOU") %>%
  clean_names() %>%
  mutate(provider_id= as.numeric(medicare_number)) %>%
  filter(is.na(medicare_number)==FALSE)

moulist <- list %>%
  select(provider_id, medicare_number, cah_name, cah_city, cah_state, cahzip)
 
nrow(moulist) 
## 2023-10-25: 1340
## 2024-05-23: 1348

no_moulist <- list %>%
  filter(!is.na(quarterly_measures)) %>%
  select(provider_id, hcahps=quarterly_measures) %>%
  mutate(hcahps= str_remove(hcahps, "Start "),
         hcahps= as.numeric(paste0(str_sub(hcahps, 4), str_sub(hcahps, 2, 3))))

#CAH with no MOU for this period --- can't use their data but need to have a report
#Even though the HCAHPS data includes multiple periods, only care about MOU from the current period
#No manual changes needed
nomou_p8 <- no_moulist %>% #7 dec 22: no mou for this quarter, etc, 2 on list -af 
  filter(hcahps > as.numeric(paste0(str_sub(quarter, end=-3), str_sub(quarter, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p7 <- no_moulist %>% 
  filter(hcahps > as.numeric(paste0(str_sub(p7_q, end=-3), str_sub(p7_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p6 <- no_moulist %>% 
  filter(hcahps > as.numeric(paste0(str_sub(p6_q, end=-3), str_sub(p6_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p5 <- no_moulist %>%  
  filter(hcahps > as.numeric(paste0(str_sub(p5_q, end=-3), str_sub(p5_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p4 <- no_moulist %>% #7 dec 22: no mou for this quarter, etc, 2 on list -af 
  filter(hcahps > as.numeric(paste0(str_sub(p4_q, end=-3), str_sub(p4_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p3 <- no_moulist %>% 
  filter(hcahps > as.numeric(paste0(str_sub(p3_q, end=-3), str_sub(p3_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p2 <- no_moulist %>% 
  filter(hcahps > as.numeric(paste0(str_sub(p2_q, end=-3), str_sub(p2_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

nomou_p1 <- no_moulist %>%  
  filter(hcahps > as.numeric(paste0(str_sub(p1_q, end=-3), str_sub(p1_q, start=-1)))) %>%
  select(provider_id) %>% 
  pull()

#recently closed CAHs, will be removed from previous Q data to prevent report generation
closed <- c(441324 , 281330 , 251329 ,251306 ,261315 ,041304 , 281321 , 421303 , 151335 , 451345 , 451360 , 441311 ,371324 ,
231317 , 
191303 ,
171340 ,
151302  ) 


hcahps_measures2 <- c("Composite 1", "Composite 2", "Composite 3", "Composite 5", "Composite 6", "Composite 7", 
                     "Q8", "Q9", "Q18", "Q19") 
```

This chunk reads in the new HCAHPS data and formats it. It's necessary to reverse the engineer the number of respondents that gave each answer because the data we receive only has the total number of respondents and the percentage that gave each answer. This is a pretty rough process because of the method in which these data are created, so I think it's most accurate to say we're reporting a general estimate rather than the exact value. There are a few addition notes about this in a document in the 2021 Q1 folder. Only the file path to the new data needs to be changed manually. 

```{r}
st_names <- tibble(cah_state=state.abb, state_name=state.name)

## 2023-10-25: pulled the function here from FMT2 because i needed to force provier_id to be numeric instea of character so it would join with MOU

read_hcahps <- function(file, joinMOU=FALSE){
  hcahps_measures <- c("Composite 1", "Composite 2", "Composite 3", "Composite 5", "Composite 6", "Composite 7",
                       "Q8", "Q9", "Q18", "Q19", "Star Rating") #also updated this for new function

  hcahps_data <- readxl::read_xlsx(paste0(fmt_folder, "Data/MBQIP Data/", file)) %>%
    janitor::clean_names() %>%
    dplyr::mutate(dplyr::across(sometimes_to_never:star_rating, as.numeric),
                  provider_id = as.numeric(provider_id) , ## added this because the provider_id wasn't joining with MOU
           period= 4,
           resp_rate= as.numeric(h_resp_rate_p)) %>%
    dplyr::select(-c(textual_completed_surveys, footnotes:h_resp_rate_p))

  if (joinMOU==TRUE){
    hcahps_frame <- tibble()
    for (m in hcahps_measures){
      temp <- moulist %>%
        dplyr::left_join(
          hcahps_data %>%
            dplyr::filter(question_id==m)) %>%
        dplyr::mutate(question_id= ifelse(is.na(question_id), m, question_id),
                      completed_surveys= ifelse(is.na(completed_surveys), "N/A", completed_surveys))

      hcahps_frame <- dplyr::bind_rows(hcahps_frame, temp)}
  } else {
    hcahps_frame <- hcahps_data %>%
      dplyr::filter(question_id %in% hcahps_measures)}

  return(hcahps_frame)
}

hcahps_raw <- read_hcahps("2023/HCAHPS/Q3 2023/HRSA_July_2024_reporting_2.xlsx", joinMOU= TRUE) ##2024-05-10: had to redo the TSV export so this is the secone xlsx file, generally there should just be one -af 


hcahps_outcomes <-  readxl::read_xlsx(paste0(fmt_folder, "Data/MBQIP Data/2023/HCAHPS/Q3 2023/HRSA_outcomes_July_2024_reporting.xlsx")) %>% 
  mutate(provider_id = as.numeric(planname)) %>% 
  select(-planname)

hcahps_raw <- hcahps_raw %>% 
  left_join(hcahps_outcomes , by = "provider_id" )

nrow(hcahps_raw) 

## 2023-10-25: 14740
##2024-05-21: 14828

#Reverse engineer the number of respondents with each answer
hcahps_new <- hcahps_raw %>%
  filter(question_id != "Star Rating") %>%
  mutate(denom= as.numeric(completed_surveys), #some of these arent that close to even numbers.. look more into it?
         allsent= round(denom/resp_rate*100, digits=0),
         num_sometimes= sometimes_to_never*denom/100,
         num_usually= usually*denom/100,
         num_always= always*denom/100,
         num_yes= yes*denom/100,
         num_no= no*denom/100,
         num_rate06= rating_0_6*denom/100,
         num_rate78= rating_7_8*denom/100,
         num_rate910= rating_9_10*denom/100,
         num_defno= definitely_no*denom/100,
         num_prob= probably_yes*denom/100,
         num_defyes= definitely_yes*denom/100) %>%
  mutate(period=8, ## 2024-05-23: changed from 4 to 8 to use EIGHT periods since the figures need them later -af 
         quarter= quarter,
         q_nonreport= ifelse(if_all(.cols= sometimes_to_never:definitely_yes, ~is.na(.)) & completed_surveys != "N/A", 1, 0) ) #,
         #q_nonreport = case_when(if_all(.cols= sometimes_to_never:definitely_yes, ~is.na(.)) & completed_surveys != "N/A" ~ 1 ,
                                # Outcome == "Responses to Few" | Outcome == "No Population" ~ 2 ,
                                # TRUE ~ 0  
       #  ) ) ## 7 dec 22: 13430 obs -af 

#separate out star ratings to add back later (otherwise bigger change might be necessary)
star_master <- hcahps_raw %>%
  filter(question_id=="Star Rating") %>% 
  select(provider_id, master_star_rating= star_rating)
```


This chunk  reads in the data created for the previous report and combines it with the new data. The reports require the new quarter of data, and the three most recent quarters that can be taken from the last report's master data file. The most recent quarterly data is referred to as "Period 4", the next most recent as "Period 3", and so on, no matter which quarter the data actually comes from. The oldest period of data is dropped and the rest are moved back by one period to make room for the new data. Then the two files are joined. Nothing should need to be manually updated, unless one-time fixes are required.

```{r}
#load data from previous report
load(paste0(fmt_folder, lastQ_data))
## 7 dec 22: if the data isn't loading "cannot open the connection" type error, check to see if the .Rdata got dropped off the end when updating above or that the file path has the correct Q and year  -af 

#adjust periods & drop old data
previous_qs <- hcahps_master_data %>%
  select(provider_id:q_nonreport) %>% #updated 5/31/22
  filter(period != 1) |>  #remove oldest period of data
  #mutate(period= period-1) #move period back 1
  mutate(period= period + 3) ## changing to an 8 period sitch, ideally after this will be able to return to the period-1 code -af 

#join all quarters- remove any closed CAHs from the old data
hcahps_cah <- hcahps_new %>% 
  bind_rows(previous_qs) %>%
  filter(!(provider_id %in% closed)) %>%
  mutate(cah_name= str_trim(cah_name)) #remove extra spaces
  

nrow(hcahps_cah) 
## 2023-10-25: 53480
## 2024-05-21: 53600 
```
2024-05: Need to add an extra FOUR points to the existing reports, we have Q3 2023 done so I'm going to go back to 2022 Q3 which should have the other 4 points we need 
```{r}
#load data from previous report
old_data <- "MBQIP Reports/Quarterly Reports/HCAHPS/2022 Q3/R/Data/hcahps_2022Q3_2023-05-16.Rdata"

load(paste0(fmt_folder, old_data))


hcahps_master_data_old  <-  hcahps_master_data |> 
  select(provider_id:q_nonreport)

hcahps_cah <-  hcahps_cah |> 
 # mutate(period = period+4) |> 
  select(provider_id:q_nonreport) |> 
  bind_rows(hcahps_master_data_old) %>%
  filter(!(provider_id %in% closed)) %>%
  mutate(cah_name= str_trim(cah_name))

unique(hcahps_cah$period) ## checking for all 8 periods -af 

```


The next chunk generates state and national estimates using the CAH data. CAHs with no MOU are not included in either calculation. If data from previous periods was added for new CAHs above, it may be necessary to exclude those from these calculations so they don't affect them. Otherwise, only the file path of the new data file needs to updated manually. This code would benefit from being adjusted, as discussed in the OPIP reports, given the time and motivation.

```{r}
hcahps_trim <- hcahps_cah %>% 
  filter(!(period==8 & provider_id %in% nomou_p8), #remove CAHs w/o MOUs
         !(period==7 & provider_id %in% nomou_p7),
         !(period==6 & provider_id %in% nomou_p6),
         !(period==5 & provider_id %in% nomou_p5),
         !(period==4 & provider_id %in% nomou_p4), #remove CAHs w/o MOUs
         !(period==3 & provider_id %in% nomou_p3),
         !(period==2 & provider_id %in% nomou_p2),
         !(period==1 & provider_id %in% nomou_p1)) %>%
  mutate(denom_adj= ifelse(q_nonreport==1, 0, denom)) #12/15
#This makes it so that percentages arent thrown off by CAHs that report surveys but nothing for at least one measure

#state estimates
hcahps_st <- hcahps_trim %>%
  group_by(cah_state, question_id, period) %>%
  summarise(st_denom= sum(denom, na.rm = TRUE),
            st_denom_adj= sum(denom_adj, na.rm = TRUE), #12/15
            st_allsent= sum(allsent, na.rm = TRUE),
            across(num_sometimes:num_defyes, ~sum(.x ,na.rm = TRUE), .names = "st_{col}")) %>% ## 2024-01-30: updated code to align with ... being deprecated for "across" in dplyr 1.1 -af 
  mutate(across(st_num_sometimes:st_num_defyes, ~round(.x/st_denom_adj*100, digits=0), .names = "rate_{col}"), #12/15
         st_resp_rate= round(st_denom/st_allsent*100, digits=0)) %>%
  rename_with(~str_remove(.x, "st_num_"), .cols= contains("rate_st")) %>%
  rename_with(~paste0("st_", .x), .cols= starts_with("rate")) %>%
  inner_join(st_names, by= "cah_state")
## 7 dec 22: 1800 obs of 30 variables -af 

#national estimates
hcahps_nat <- hcahps_trim %>%
  group_by(question_id, period) %>%
  summarise(across(num_sometimes:num_defyes, ~sum(.x , na.rm = TRUE), .names = "nat_{col}"),
            nat_denom= sum(denom, na.rm=TRUE),
            nat_denom_adj= sum(denom_adj, na.rm = TRUE), #12/15
            nat_allsent= sum(allsent, na.rm = TRUE)) %>%
  mutate(across(nat_num_sometimes:nat_num_defyes, ~round(.x/nat_denom_adj*100, digits=0), .names = "rate_{col}"), #12/15
         nat_resp_rate= round(nat_denom/nat_allsent*100, digits=0)) %>%
  rename_with(~str_remove(.x, "nat_num_"), .cols= contains("rate_nat")) %>%
  rename_with(~paste0("nat_", .x), .cols= starts_with("rate"))
## 7 dec 22: 40 obs of 28 variables -af 

#merge three levels of data
hcahps_master_data <- hcahps_cah %>%
  inner_join(hcahps_st, by= c("cah_state", "question_id", "period")) %>%
  inner_join(hcahps_nat, by= c("question_id", "period")) %>%
  inner_join(star_master, by= "provider_id") %>%
  select(-contains("denom_adj")) %>% 
  mutate(cah_name= str_replace_all(cah_name, "&", "and"),
         cah_name= str_replace_all(cah_name, "#", "") ,
        # cah_name= str_replace_all(cah_name, "'", "\\'") , ## seeing if this fixes the apostrophe problem
          ps_flag= case_when( #used to assign "*" later
      Outcome == "Responses to Few" | Outcome ==  "No Population" ~ 1, ## 25 april 23: updated from new HCAHPS footnotes and submission data per discussion with Megan -af 
      TRUE ~ 0)) 
#These characters are escaped in Latex, which causes an error when they're inserted into the figure titles
#For now, this changes them to avoid that. There's probably way to actually fix the issue and maintain the
#original symbols, but I haven't gotten it to work. Typically, would use "\\" before the symbol to escape it.
#One of the backslashes will escape in Latex, the other is to escape that backslash in R.



#dir.create(glue::glue("{fmt_folder}/MBQIP Reports/Quarterly Reports/HCAHPS/{quarter}/R/Data") , recursive = TRUE)
dir.create(glue::glue(here::here("R/Data/{quarter}") , recursive = TRUE))

##2024-01-30: updated the file paths to be automatic instead of manually changing the quarter in every file path -af 
#save(hcahps_master_data, file = glue::glue("{fmt_folder}/MBQIP Reports/Quarterly Reports/HCAHPS/{quarter}/R/Data/hcahps_{quarter}_{Sys.Date()}.RData"))

save(hcahps_master_data , file = glue::glue(here::here("R/Data/{quarter}/hcahps_update_{quarter}_{Sys.Date()}.RData")))
```


The next chunk will use the data to produce the PDF reports. There is quite a bit that needs to be manually updated at the beginning of the chunk. There may be a better way to do this. Make sure the filepath is set to the data created for this quarter so you can read that in without having to recreate the entire file by rerunning the chunks above. Updates to quarters and folders are self-explanatory. Make sure the report is drawing from the most recent benchmarks document, and that it isn't time to update the benchmarks for this report.

Templates will be used to create both state and CAH-level reports. No regular updates are needed to the templates between reports, but sometimes there may be changes that need to be made to the cover page text. Running each loop should create the reports for all states or CAHs. It can take several hours to create all CAH reports.

```{r}
#the data file for this quarter
#load(glue::glue("{fmt_folder}/MBQIP Reports/Quarterly Reports/HCAHPS/{quarter}/R/Data/hcahps_{quarter}_2024-01-30.RData"))  

load(glue::glue(here::here("R/Data/{quarter}/hcahps_update_{quarter}_2024-05-23.RData")))

# ## 16 may dataset has the \\' in CAH names, see if that helps , also used the OLD MOU list (didn't fix it with either of those changes )
# load(paste0(fmt_folder, "MBQIP Reports/Quarterly Reports/HCAHPS/2022 Q3/R/Data/hcahps_2022Q3_2023-05-16.RData"))  
# 

## removing apostrophes for the meantime til I can figure out why they don't work 
hcahps_master_data <- hcahps_master_data %>% 
  mutate(cah_name= str_replace_all(cah_name, "'", "") ) 


# hcahps_master_data2 <- hcahps_master_data %>% 
#   mutate(resp_rate = case_when(ps_flag == 1 ~ "*" ,
#                                TRUE ~ resp_rate))

##2024-01-30: updated directory creation to use glue+quarter so it doesn't have to be manually changed every quarter -af 
#dir.create(glue::glue("C:/Users/furuk015/Desktop/HCAHPS/reports/HCAHPS_{quarter}"))
dir.create("C:/Users/furuk015/Desktop/projects/MBQIP_update/reports" , recursive = TRUE)
#report_directory <-here::here(glue::glue("reports/HCAHPS_{quarter}"))
report_directory <-here::here(glue::glue("C:/Users/furuk015/Desktop/projects/MBQIP_update/reports"))

report_period <- "Current Reporting Period: Q4 2022 - Q3 2023"
#report_period <- "Current Reporting Period: Q4 2020, Q1 2021, Q3 2021" #used in alt report text for Q32021 reports
p8 <- "Q3 2023"
p7 <- "Q2 2023"
p6 <- "Q1 2023"
p5 <- "Q4 2022"
p4 <- "Q3 2022"
p3 <- "Q2 2022"
p2 <- "Q1 2022"
p1 <- "Q4 2021"

range8 <- "Q4 2022 - Q3 2023"
range7 <- "Q3 2022 - Q2 2023"
range6 <- "Q2 2022 - Q1 2023"
range5 <- "Q1 2022 - Q4 2022" 
range4 <- "Q4 2021 - Q3 2022"
range3 <- "Q3 2021 - Q2 2022"
range2 <- "Q2 2021 - Q1 2022"
range1 <- "Q1 2021 - Q4 2021" 



#Make sure no updates are needed to the benchmarks
#This should only be necessary in the Q1 reports, when new benchmarks from the previous year's data will be created
bms <- readxl::read_xlsx(paste0(fmt_folder, "MBQIP Reports/Report Creation and Processes/Report Benchmarks_10_04_23.xlsx"))

#these five values affect the spreadsheets
start_q <- "3Q2022"
start_d <- "07/01/2022"
end_q <- "2Q2023"
end_d <- "06/31/2023"
current_file <- "2023/HCAHPS/Q2 2023/HRSA_April_2024_reporting.xlsx"

###################### ^ Everything above needs to be manually updated ^ #######################

p8z <- paste0(str_sub(range8, end=9), "z", str_sub(range8, start=11))
p7z <- paste0(str_sub(range7, end=9), "z", str_sub(range7, start=11))
p6z <- paste0(str_sub(range6, end=9), "z", str_sub(range6, start=11))
p5z <- paste0(str_sub(range5, end=9), "z", str_sub(range5, start=11))
p4z <- paste0(str_sub(range4, end=9), "z", str_sub(range4, start=11))
p3z <- paste0(str_sub(range3, end=9), "z", str_sub(range3, start=11))
p2z <- paste0(str_sub(range2, end=9), "z", str_sub(range2, start=11))
p1z <- paste0(str_sub(range1, end=9), "z", str_sub(range1, start=11))

states <- hcahps_master_data %>% distinct(cah_state) %>% unlist(use.names = FALSE)
folder <- paste(str_sub(quarter, end= 4), str_sub(quarter, -2))

states <- "MI" 
# STATE REPORTS #
dir.create(glue::glue("{report_directory}/STATE REPORTS"))
for (st in states){
  state_data <- hcahps_master_data %>%
    filter(cah_state==st) %>%
    select(cah_state, period, quarter, question_id, st_denom:nat_resp_rate ) %>%
    group_by(period, quarter, cah_state, state_name, question_id ) %>%
    summarise(across(st_denom:nat_resp_rate, median, na.rm=TRUE)) %>%
    ungroup() %>%
    inner_join(bms, by= c("question_id"="measure"))
  state_name <- unique(state_data$state_name)[1]
    rmarkdown::render(input = here::here("scripts/HCAHPS_State_Report_Template.Rmd"), 
                    output_format = "pdf_document",
                    output_dir = here::here(glue::glue("{report_directory}/STATE REPORTS")) ,
                  
                    output_file = glue::glue("{st}_HCAHPS_{p4}.pdf"))
  }



# CAH REPORTS #
for (st in states){
  state_data <- hcahps_master_data %>% filter(cah_state==st)
  cah_list <- unique(state_data$medicare_number)
  ncah <- length(cah_list)
  dir.create(paste0(report_directory,"/",st))
  for (i in cah_list){
    cah <- state_data %>% filter(medicare_number== i) %>% inner_join(bms, by= c("question_id"="measure"))
    cah_id <- unique(cah$medicare_number)
    name <- cah %>% filter(period==max(period)) %>% select(cah_name) %>% distinct() %>% unlist(use.names = FALSE) 
    hospinfo <- paste0(cah_id, ": ", name)[1]
    hospgeo <- paste0(unique(cah$cah_city)[1], ", ", unique(cah$cah_state), ", ", unique(cah$cahzip))[1]
    count <- cah %>% filter(period==8) %>% distinct(completed_surveys) %>% unlist(use.names = FALSE)
    #maybe add some rounding for 1000+
   new_count <- cah %>% filter(period==8) %>% distinct(ps_flag) %>% unlist(use.names = FALSE)
   count2 <- ifelse(new_count== 1, "*", count) ## 28 aug 23: updated to try to replace NA with * when appropriate using the ps_flag
    cah_resp <- cah %>% filter(period==8) %>% distinct(resp_rate) %>% unlist(use.names = FALSE)
    new_cah_resp<- cah %>% filter(period==8) %>% distinct(ps_flag) %>% unlist(use.names = FALSE)
    response <- ifelse(is.na(cah_resp)==TRUE, "N/A", round_perc(cah_resp/100))
    response_new <- ifelse(new_cah_resp== 1, "*", response) ## 28 aug 23: updated to try to replace NA with * when appropriate using the ps_flag
    cah_star <- cah %>% distinct(master_star_rating) %>% unlist(use.names = FALSE)
    star <- ifelse(is.na(cah_star)==TRUE, "N/C", as.character(cah_star))
    state_name <- unique(state_data$state_name)[1]
    #rmarkdown::render(#input = paste0(fmt_folder, "MBQIP Reports/Quarterly Reports/HCAHPS/", folder, "/R/HCAHPS CAH Report Template.Rmd"),
                       rmarkdown::render(input = here::here("R/hcahps_cah_template.Rmd"), ## updates2 has the new * version 
                       #input = paste0("C:/Users/furuk015/Desktop/projects/MBQIP_update/R/hcahps_cah_template.Rmd"),
                      output_format = "pdf_document",
                      output_file = paste0(st, "_", cah_id,"_", name, "_HCAHPS_", p8,".pdf"),
                     # output_dir = paste0(report_directory,"/",st))
                       output_dir = here::here(glue::glue("{report_directory}/{st}")))
  }
}

```