---
title: "**Hospital-Level HCAHPS Report**"
author: "`r report_period`"
date: "**`r name`**"
output: pdf_document
classoption: landscape
geometry: margin=0.5in
fontsize: 11.5pt
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{titling}
- \pretitle{\begin{center}\LARGE\includegraphics[width=10cm]{flex_full_logo.png}\\[\bigskipamount]}
- \posttitle{\end{center}}
- \renewcommand\maketitlehooka{\vspace{-5ex}}
- \renewcommand\maketitlehookb{\vspace{-5ex}}
- \renewcommand\maketitlehookc{\vspace{-5ex}}
---
\renewcommand{\arraystretch}{1.7}

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE , warning = FALSE)
```

```{r quarters update, include=FALSE}
#if a cAH doesn't have rows for all four quarters (was added recently) it will not have enough data for the trend figures
#which creates an error. this code will add necessaery rows when needed
quarterly_periods <- c(8, 7, 6 , 5, 4, 2, 3, 1)

for (per in quarterly_periods){
  for (m in hcahps_measures2){
    cah_temp <- cah %>% filter(question_id==m)
    if (!(per %in% cah_temp$period)){
        st_nt <- state_data %>% #get state and natl data for period, measure
            filter(period==per,
                   question_id==m) %>%
            slice(1) %>%
            select(question_id, period, st_denom:master_star_rating) %>%
          mutate(provider_id= as.numeric(i))
        
        cah <- cah %>% bind_rows(st_nt) #add s/n data to CAH data frame

    }
  }
}
```

```{r setup composite 1 , include=FALSE }
composites <- c("Composite_1", "Composite_2", "Composite_3", "Composite_5" , "Q8" , "Q9")

#trend figure
hcahps_labs <- c("Nurse Communication", "Doctor Communication", "Staff Responsiveness", "Medicine Communication", "Cleanliness",
                 "Quietness", "Discharge Info", "Care Transition", "Patient Rating", "Recommendation")

hcahps_measures <- c("Composite_1", "Composite_2", "Composite_3", "Composite_5" , "Q8", "Q9", "Composite_6", "Composite_7", "Q18", "Q19")


 cah <- cah |> 
   mutate(question_id = str_replace_all(question_id , " " , "_") ,
         question_label = factor( question_id , 
levels = c("Composite_1", "Composite_2", "Composite_3", "Composite_5" , "Composite_6" , "Composite_7" , "Q8" , "Q9" , "Q18" , "Q19") , 
                                   labels = c(
                                     "Composite 1 (Q1 to Q3) Communication with Nurses",
                                     "Composite 2 (Q5 to Q7) Communication with Doctors",
                                    "Composite 3 (Q4 & Q11) Responsiveness of Hospital Staff",
                                     "Composite 5 (Q13 & Q14) Communication about Medicines" ,
                                     "Composite 6 (Q16 & Q17) Discharge Information" ,
                                     "Composite 7 (Q20 to Q22) Care Transition" ,
                                     
                "Q8  Cleanliness of Hospital",
                "Q9  Quietness of Hospital",
                "Q18  Overall Rating of Hospital (0 = worst hospital, 10 = best hospital)",
                "Q19  Willingness to Recommend This Hospital"
                )))

composite_rows <- cah %>%
  filter(question_id %in% composites, period==8) %>% 
  select(medicare_number, question_id , question_label ,  star_rating, sometimes_to_never:always, st_rate_sometimes:st_rate_always,
         nat_rate_sometimes:nat_rate_always, benchmark , ps_flag) %>% #edited 11/30
  #arrange(-question_id) #should maybe add a check to make sure composite are in correct order
  mutate(across(sometimes_to_never:benchmark, ~ifelse(is.na(.x), "N/A", rnd_perc(.x/100))), #11/30 (inc rounding change)
         across(sometimes_to_never:always, ~ifelse(medicare_number %in% nomou_p8, "#", .x)), ## 19 dec 22: I think the Hawaii CAHs that don't show up have something to do with how # vs NA is approached for the tables, look into where and why they are difrferent -af
         across(sometimes_to_never:always, ~ifelse(ps_flag == 1, "*", .x)) , ## 26 apr 23: updating to try to implement stars for some CAHs
         star_rating= ifelse(is.na(star_rating), "N/C", as.character(star_rating))) %>%
  select(-medicare_number , -ps_flag)

c6_row <- cah %>%
  filter(question_id== "Composite_6", period==8) %>% 
  select(question_id , question_label , star_rating, no, yes, st_rate_no, st_rate_yes, nat_rate_no, nat_rate_yes, benchmark , ps_flag) %>% #11/30
  ## 26 apr 23: updating to try to implement stars for some CAHs , added ps_flag -af 
  mutate(across(no:benchmark, ~ifelse(is.na(.x), "N/A", rnd_perc(.x/100))), #11/30
         across(no:yes, ~ifelse(as.numeric(cah_id) %in% nomou_p8, "#", .x)),
         #the above line will technically dup first row for all rows.. but only 1 row for all below, so okay for now
        across(no:yes, ~ifelse(ps_flag == 1, "*", .x)), ## 26 apr 23: updating to try to implement stars for some CAHs
         star_rating= ifelse(is.na(star_rating), "N/C", as.character(star_rating))) %>% 
  select(-ps_flag)

#same as state, var values are named wrong but data is correct  
c7_row <- cah %>%
  filter(question_id== "Composite_7", period==8) %>% 
  select(question_id   , question_label , star_rating, sometimes_to_never:always, st_rate_sometimes:st_rate_always,
         nat_rate_sometimes:nat_rate_always, benchmark , ps_flag) %>% #11/30
  mutate(across(sometimes_to_never:benchmark, ~ifelse(is.na(.x), "N/A", rnd_perc(.x/100))), #11/30
         across(sometimes_to_never:always, ~ifelse(as.numeric(cah_id) %in% nomou_p8, "#", .x)),
         across(sometimes_to_never:always, ~ifelse(ps_flag == 1, "*", .x)), ## 26 apr 23: updating to try to implement stars for some CAHs
         star_rating= ifelse(is.na(star_rating), "N/C", as.character(star_rating))) %>%
  select(-ps_flag) %>% 
  rbind(rep(" ", 11)) #11/30
  
q18_row <- cah %>%
  filter(question_id== "Q18", period==8) %>% 
  select(question_id , question_label, star_rating, rating_0_6:rating_9_10, st_rate_rate06:st_rate_rate910, nat_rate_rate06:nat_rate_rate910, benchmark , ps_flag) %>% #11/30
  mutate(across(rating_0_6:benchmark, ~ifelse(is.na(.x), "N/A", rnd_perc(.x/100))), #11/30
         across(rating_0_6:rating_9_10, ~ifelse(as.numeric(cah_id) %in% nomou_p8, "#", .x)),
         across(rating_0_6:rating_9_10, ~ifelse(ps_flag == 1, "*", .x)) ,
         star_rating= ifelse(is.na(star_rating), "N/C", as.character(star_rating))) %>% 
    select(-ps_flag)
  
q19_row <- cah %>%
  filter(question_id== "Q19", period==8) %>% 
  select(question_id , question_label, star_rating, definitely_no:definitely_yes, st_rate_defno:st_rate_defyes, nat_rate_defno:nat_rate_defyes, benchmark , ps_flag) %>% #11/30
  mutate(across(definitely_no:nat_rate_defyes, ~ifelse(is.na(.x), "N/A", rnd_perc(.x/100))), #11/30
         across(definitely_no:definitely_yes, ~ifelse(as.numeric(cah_id) %in% nomou_p8, "#", .x)),
         across(definitely_no:definitely_yes, ~ifelse(ps_flag == 1, "*", .x)) ,
         benchmark= ifelse(is.na(benchmark), " ", round_perc(benchmark/100)), #11/30
         star_rating= ifelse(is.na(star_rating), "N/C", as.character(star_rating))) %>%
  select(-ps_flag) %>% 
  set_colnames(names(q18_row)) 



## 2024-03-01: wrote a function for the first composites, could maybe make it a loop at some point? but this works for now I think -af  
composite_table <- function(x) {
  composite_data   <- composite_rows |> 
    filter(question_id== x) 
  
  table <- composite_data |> 
    select(-question_id) |> 
  gt(rowname_col = "question_label")  |> 
  tab_stubhead(label = md("**HCAHPS Composite**"))|> 
    gt::cols_width(question_label ~ px(40) , ##2024-01-26: see how wide we can go! -af 
                 everything() ~px(40)) |> 
  tab_spanner(
    label = md("**HCAHPS Star Rating**") ,
    columns = "star_rating" ,
    id = "star_id"
  ) |> 
  tab_spanner(
    label = md("**Your Hospital's Adjusted Score**") ,
    columns = c(sometimes_to_never , usually , always) ,
    id = "hsp_id"
  ) |> 
  tab_spanner(
    label = md("**Your State's CAH Data**") ,
    columns = c(st_rate_sometimes , st_rate_usually , st_rate_always) ,
    id = "state_id"
  ) |> 
  tab_spanner(
    label = md("**National CAH Data**") ,
    columns = c(nat_rate_sometimes , nat_rate_usually , nat_rate_always) ,
    id = "nat_id"
  ) |> 
  tab_spanner(
    label = md("**Benchmark**") ,
    columns = "benchmark"  ,
    id = "benchmark_id" 
  ) |> 
  cols_label(
    star_rating = "Star Rating (0-5)" , 
    contains("sometimes") ~ "Sometimes to Never" ,
    contains("usually") ~ "Usually" ,
    contains("always") ~ "Always" ,
    benchmark = "Always"
  ) |> 
  tab_style(
    style = cell_borders(
      sides = "left" ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("sometimes") 
  )) |> 
  tab_style(
    style = cell_borders(
      sides = "right" ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("always") 
  ))  |> 
    tab_options(table.width = pct(100))
  
  
}

table1 <- composite_table("Composite_1")



## 2024-05-21: figure 1 and 2 should also be able to be done as a function but I think I have to write the figure first -af

trend_data <- cah %>%
  mutate(
    cah_est= case_when(
      #always != 0 ~ always, ## 13 dec 22: is this why the AK 021307 CAH trendline is wrong, look at it -af
      always >= 0 ~ always, ## 19 dec 22: trying just this one to see -af
      ## doesn't appear to do anything at all? -af
      yes  != 0 ~ yes,
      rating_9_10   != 0 ~ rating_9_10,
      definitely_yes != 0 ~ definitely_yes),
    ########added 1/26/21 ################## -- added state line
    st_est= case_when(
      st_rate_always != 0 ~ st_rate_always,
      st_rate_yes  != 0 ~ st_rate_yes,
      st_rate_rate910  != 0  ~ st_rate_rate910,
      st_rate_defyes  != 0 ~ st_rate_defyes),
    ##########################################
    nat_est= case_when(
      nat_rate_always != 0 ~ nat_rate_always,
      nat_rate_yes  != 0 ~ nat_rate_yes,
      nat_rate_rate910  != 0  ~ nat_rate_rate910,
      nat_rate_defyes  != 0 ~ nat_rate_defyes)) %>%
  select(provider_id, period, question_id, cah_est, st_est, nat_est) %>% #edited 1/26/21
  pivot_longer(cols= contains("_est"), names_to= "cah_state", values_to= "est") %>% ## 19 dec 22: trend data keeps the 0 here, so somehwere after this it turns a reported zero into an NA, which messes up the trendline -af
  mutate( #edited all of this, 1/26/21
    cah_state= case_when(
      str_detect(cah_state, "nat") ~ "U.S.",
      str_detect(cah_state, "st_est") ~ st,
      str_detect(cah_state, "cah") ~ "Your Hospital"),
    cah_state= factor(cah_state, c("U.S.", st, "Your Hospital")),
    est= case_when( #added 3/24/22.. there are a couple previous reports with errors, such as 011306 because this was missing
      cah_state=="Your Hospital" & period==8 & provider_id %in% nomou_p8 ~ -999, #fixed this 5/31/22, likely errors in previous reports?
      cah_state=="Your Hospital" & period==7 & provider_id %in% nomou_p7 ~ -999,
      cah_state=="Your Hospital" & period==6 & provider_id %in% nomou_p6 ~ -999,
      cah_state=="Your Hospital" & period==5 & provider_id %in% nomou_p5 ~ -999,
      cah_state=="Your Hospital" & period==4 & provider_id %in% nomou_p4 ~ -999, #fixed this 5/31/22, likely errors in previous reports?
      cah_state=="Your Hospital" & period==3 & provider_id %in% nomou_p3 ~ -999,
      cah_state=="Your Hospital" & period==2 & provider_id %in% nomou_p2 ~ -999,
      cah_state=="Your Hospital" & period==1 & provider_id %in% nomou_p1 ~ -999,
      TRUE ~ est),
     est= ifelse(est==-999, NA, est)) %>% 
  select(-provider_id)


###################################################
## necesasry code for charts below ##
three_pal <- c('#8856a7','#a4e05e','#43a2ca')
addline_format <- function(x,...){
    gsub('z','\n',x)
}
#############################################


plots_list <- list() 

for (i in hcahps_measures){
  figure_data <- trend_data |> 
  filter(question_id== i) 
  
  composite_figure <- ggplot() +
  geom_line(data= figure_data, aes(x= period, y=est, group= cah_state, color= cah_state, 
                                        linetype= cah_state), size= 1.25) +
  geom_point(data= filter(figure_data, cah_state == "Your Hospital"), aes(x= period, y=est, group= question_id), 
               shape=21, size=2, fill=base_blue) +
  geom_text(data= filter(figure_data, cah_state == "Your Hospital"), 
            aes(x= period, y= est, label= rnd_perc(est, dec=F),
                vjust= vjust_hcahps2(figure_data, upper=.91)
                ), 
            size=4) +
  #changed filtering above ^
  #scale_color_manual(values = c("#60AFFE", "#3486c5")) +
  scale_color_manual(values = three_pal) +
  #scale_linetype_manual(values= c("dashed", "solid")) +
  scale_linetype_manual(values= c("dashed", "dotdash", "solid")) +
  scale_y_continuous(limits= c(0,100), 
                     breaks= c(0, 50, 100),
                     expand = expansion(mult = c(0, .1))) +
  scale_x_continuous(breaks = c(1:8) ,
                     labels= addline_format(c("1"= p1z, "2"= p2z, "3"= p3z, "4"= p4z , "5"= p5z, "6"= p6z, "7"= p7z, "8"= p8z))) +
  labs(x="", y="Percentage", color="", linetype="") +
  guides(color = guide_legend(nrow = 1), fill="none") +
  theme_classic() +
  theme(
    axis.text.y = element_text(size=12, color="black"),
    axis.text.x = element_text(size=10, color="black", angle=45, hjust=1),
    axis.title = element_text(size=13, color="black"),
    strip.text = element_text(size=13),
    strip.background = element_rect(linetype = "blank"),
    legend.background=element_blank(),
    legend.margin=margin(c(-15,-15,-15,-15)),
    legend.spacing.x = unit(0, "mm"),
    legend.spacing.y = unit(0, "mm"),
    #legend.position = c(.5, 1.05),
    legend.position = "top",
    legend.text = element_text(size=12),
    legend.key.size =  unit(3.5, "lines"))
  
  plots_list[[i]] <- composite_figure
  
}

print(plots_list$Composite_1)

```

```{r composite2 setup}

table2 <- composite_table("Composite_2")


```


```{r setup composite 3}
table3 <- composite_table("Composite_3")
```

```{r setup composite 5}
table5 <- composite_table("Composite_5")


```


```{r q8 setup}


q89_table <- function(x ) {
  composite_data   <- composite_rows |> 
    filter(question_id== x) 
  
  comp_id <- unique(composite_data$question_id)[1]
  
  table <- composite_data |> 
    select(-question_id) |> 
  gt(rowname_col = "question_label")  |> 
  tab_stubhead(label = md("**Hospital Environment Items**"))|> 
    gt::cols_width(question_label ~ px(60) , 
                 everything() ~px(40)) |> 
  tab_spanner(
    label = md("**HCAHPS Star Rating**") ,
    columns = "star_rating"
  ) |> 
  tab_spanner(
    label = md("**Your Hospital's Adjusted Score**") ,
    columns = c(sometimes_to_never , usually , always)
  ) |> 
  tab_spanner(
    label = md("**Your State's CAH Data**") ,
    columns = c(st_rate_sometimes , st_rate_usually , st_rate_always) 
  ) |> 
  tab_spanner(
    label = md("**National CAH Data**") ,
    columns = c(nat_rate_sometimes , nat_rate_usually , nat_rate_always) ,
    id = "nat_data"
  ) |> 
  tab_spanner(
    label = md("**Benchmark**") ,
    columns = "benchmark"  
  ) |> 
  cols_label(
    star_rating = "Star Rating (0-5)" , 
    contains("sometimes") ~ "Sometimes to Never" ,
    contains("usually") ~ "Usually" ,
    contains("always") ~ "Always" ,
    benchmark = "Always"
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("left") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("sometimes") 
  )) |> 
  tab_style(
    style = cell_borders(
      sides = c("right") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("always") 
  ))
    
  
  
}

tableq8 <- q89_table("Q8")
```


```{r setup q9}

tableq9 <- q89_table("Q9")

```

```{r setup composite 6}
comp6_table <- function(x ) {
  composite_data   <- c6_row |> 
    filter(question_id== x) 
  
  comp_id <- unique(composite_data$question_id)[1]
  
  table <- composite_data |> 
    select(-question_id) |> 
  gt(rowname_col = "question_label")  |> 
  tab_stubhead(label = md("**Discharge Information Composite**"))|> 
    gt::cols_width(question_label ~ px(60) , 
                 everything() ~px(40)) |> 
  tab_spanner(
    label = md("**HCAHPS Star Rating**") ,
    columns = "star_rating"
  ) |> 
  tab_spanner(
    label = md("**Your Hospital's Adjusted Score**") ,
    columns = c("no" , "yes")
  ) |> 
  tab_spanner(
    label = md("**Your State's CAH Data**") ,
    columns = c(st_rate_no , st_rate_yes) 
  ) |> 
  tab_spanner(
    label = md("**National CAH Data**") ,
    columns = c(nat_rate_no, nat_rate_yes) ,
    id = "nat_data"
  ) |> 
  tab_spanner(
    label = md("**Benchmark**") ,
    columns = "benchmark"  
  ) |> 
  cols_label(
    star_rating = "Star Rating (0-5)" , 
    contains("no") ~ "No" ,
    contains("yes") ~ "Yes" ,
    benchmark = "Yes"
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("left") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("no") 
  )) |> 
  tab_style(
    style = cell_borders(
      sides = c("right") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("yes") 
  ))
    
  
  
}

table6 <- comp6_table("Composite_6")

```

```{r setup comp 7}
comp7_table <- function(x ) {
  composite_data   <- c7_row |> 
    filter(question_id== x) 
  
  comp_id <- unique(composite_data$question_id)[1]
  
  table <- composite_data |> 
    select(-question_id) |> 
  gt(rowname_col = "question_label")  |> 
  tab_stubhead(label = md("**Care Transition Composite**"))|> 
    gt::cols_width(question_label ~ px(60) , 
                 everything() ~px(40)) |> 
  tab_spanner(
    label = md("**HCAHPS Star Rating**") ,
    columns = "star_rating"
  ) |> 
  tab_spanner(
    label = md("**Your Hospital's Adjusted Score**") ,
    columns = c(sometimes_to_never , usually , always)
  ) |> 
  tab_spanner(
    label = md("**Your State's CAH Data**") ,
    columns = c(st_rate_sometimes , st_rate_usually , st_rate_always) 
  ) |> 
  tab_spanner(
        label = md("**National CAH Data**") ,
    columns = c(nat_rate_sometimes , nat_rate_usually , nat_rate_always) ,
    id = "nat_data"
  ) |> 
  tab_spanner(
    label = "Benchmark" ,
    columns = "benchmark"  
  ) |> 
  cols_label(
    star_rating = "Star Rating (0-5)" , 
    contains("sometimes") ~ "Disagree to Strongly Disagree" ,
    contains("usually") ~ "Agree" ,
    contains("always") ~ "Strongly Agree" ,
    benchmark = "Strongly Agree"
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("left") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("sometimes") 
  )) |> 
  tab_style(
    style = cell_borders(
      sides = c("right") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("always") 
  ))
    
  
  
}

table7 <- comp7_table("Composite_7")
```

```{r q18 setup}

q18_function <- function(x ) {
  composite_data   <- q18_row |> 
    filter(question_id== x) 
  
  comp_id <- unique(composite_data$question_id)[1]
  
  table <- composite_data |> 
    select(-question_id) |> 
  gt(rowname_col = "question_label")  |> 
  tab_stubhead(label = md("**HCAHPS Global Items**"))|> 
    gt::cols_width(question_label ~ px(60) , 
                 everything() ~px(40)) |> 
  tab_spanner(
    label = md("**HCAHPS Star Rating**") ,
    columns = "star_rating"
  ) |> 
  tab_spanner(
    label = md("**Your Hospital's Adjusted Score**") ,
    columns = c(rating_0_6:rating_9_10)
  ) |> 
  tab_spanner(
     label = md("**Your State's CAH Data**") ,
    columns = c(st_rate_rate06:st_rate_rate910) 
  ) |> 
  tab_spanner(
    label = md("**National CAH Data**") ,
    columns = c(nat_rate_rate06:nat_rate_rate910) ,
    id = "nat_data"
  ) |> 
  tab_spanner(
    label = md("**Benchmark**") ,
    columns = "benchmark"  
  ) |> 
  cols_label(
    star_rating = "Star Rating (0-5)" , 
    contains("6") ~ "0-6 rating" ,
    contains("7") ~ "7-8 rating" ,
    contains("9") ~ "9-10 rating" ,
    benchmark = "9-10 rating"
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("left") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("6") 
  )) |> 
  tab_style(
    style = cell_borders(
      sides = c("right") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("9") 
  ))
    
  
  
}

q18_table <- q18_function("Q18")

```


```{r q19 setup}
q19_function <- function(x ) {
  composite_data   <- q19_row |> 
    filter(question_id== x) 
  
  comp_id <- unique(composite_data$question_id)[1]
  
  table <- composite_data |> 
    select(-question_id) |> 
  gt(rowname_col = "question_label")  |> 
  tab_stubhead(label = md("**HCAHPS Global Items**"))|> 
    gt::cols_width(question_label ~ px(60) ,
                 everything() ~px(40)) |> 
  tab_spanner(
    label = md("**HCAHPS Star Rating**") ,
    columns = "star_rating"
  ) |> 
  tab_spanner(
     label = md("**Your Hospital's Adjusted Score**") ,
    columns = c(rating_0_6:rating_9_10)
  ) |> 
  tab_spanner(
    label = md("**Your State's CAH Data**") ,
    columns = c(st_rate_rate06:st_rate_rate910) 
  ) |> 
  tab_spanner(
    label = md("**National CAH Data**") ,
    columns = c(nat_rate_rate06:nat_rate_rate910) ,
    id = "nat_data"
  ) |> 
  tab_spanner(
   label = md("**Benchmark**") ,
    columns = "benchmark"  
  ) |> 
  cols_label(
    star_rating = "Star Rating (0-5)" , 
    contains("6") ~ "Definitely Not or Probably Not" ,
    contains("7") ~ "Probably" ,
    contains("9") ~ "Definitely" ,
    benchmark = "No Benchmark"
  ) |> 
  tab_style(
    style = cell_borders(
      sides = c("left") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("6") 
  )) |> 
  tab_style(
    style = cell_borders(
      sides = c("right") ,
      color = "gray" ,
      weight = px(1)) ,
    locations = cells_body(columns = contains("9") 
  ))
    
  
  
}

q19_table <-  q19_function("Q19")

```

The Medicare Beneficiary Quality Improvement Program (MBQIP) focuses on quality improvement efforts in the 45 states that participate in the Medicare Rural Hospital Flexibility (Flex) Program. Through Flex, MBQIP supports more than 1,350 small hospitals certified as rural Critical Access Hospitals (CAHs) in voluntarily reporting quality measures that are aligned with those collected by the Centers for Medicare and Medicaid Services (CMS) and other Federal programs.   
The Federal Office of Rural Health Policy (FORHP) tasked the Flex Monitoring Team with producing a set of hospital-level reports for the core MBQIP measures. 

Data for the Patient Experience MBQIP Domain are included here, specifically for the Hospital Consumer Assessment of Healthcare Providers and Systems (HCAHPS) measure. HCAHPS is a quarterly measure, and all data in the report are updated each quarter. This measure has several components included in this report:

*	HCAHPS Composite 1: Q1 to Q3, Communication with Nurses
*	HCAHPS Composite 2: Q5 to Q7, Communication with Doctor
*	HCAHPS Composite 3: Q4 & Q11, Responsiveness of Hospital Staff
*	HCAHPS Composite 5: Q13 & Q14, Communication about Medicines
*	HCAHPS Composite 6: Q16 & Q17, Discharge Information
*	HCAHPS Composite 7: Q20 to Q22, Care Transition
*	HCAHPS Q-8: Cleanliness of Hospital Environment
*	HCAHPS Q-9: Quietness of Hospital Environment
*	HCAHPS Q-18: Overall Rating of Hospital
*	HCAHPS Q-19: Willingness to Recommend This Hospital


Data for all other MBQIP Domains and measures are released separately each quarter in the MBQIP Measures Reports. For more information regarding the data and calculations, please reference the Appendix at the end of this document.

\newpage

**HCAHPS Composite 1: Communication with Nurses**
```{r composite1 table }
table1
```

```{r composite1 figure}
print(plots_list$Composite_1)
```

**HCAHPS Composite 2: Communication with Doctor**
```{r composite2 table}
table2 

```

```{r composite2 figure}
print(plots_list$Composite_2)
```

**HCAHPS Composite 3: Responsiveness of Hospital Staff**
```{r composite3 table}
 table3
```

```{r composite3 figure}
print(plots_list$Composite_3)
```

**HCAHPS Composite 5: Communication about Medicines**

```{r composite5 table }
table5
```

```{r composite5 figure}
print(plots_list$Composite_5)
```

\newpage


**HCAHPS Composite 6: Discharge Information**

```{r composite 6 table}

table6

```

```{r composite 6 figure}
print(plots_list$Composite_6)
```

\newpage

**HCAHPS Composite 7: Care Transition**

```{r composite 7 table}

table7
```

```{r composite 7 figure}
print(plots_list$Composite_7)
```

\newpage

**HCAHPS Q-8: Cleanliness of Hospital Environment**


```{r q8 table}

tableq8
```

```{r q8 figure}
print(plots_list$Q8)
```

**HCAHPS Q9: Quietness of Hospital Environment**

```{r q9 table}

tableq9
```

```{r figure}
print(plots_list$Q9)
```


\newpage


**HCAHPS Q18: Overall Rating of Hospital**

```{r q18 table}

q18_table
```

```{r q18 figure}
print(plots_list$Q18)
```

**HCAHPS Q-19: Willingness to Recommend This Hospital**

```{r q19 table}

q19_table
```

```{r q19 figure}
print(plots_list$Q19)
```

\newpage
\begin{center}
{\bfseries\LARGE Appendix}
\end{center}

\fontsize{12}{13}

**General Report Information**
For the measures in this report, hospital-level data are included for the current reporting period, which includes four rolling quarters. Hospital-level data include: 

*	The number of completed surveys - the number of participants who returned the survey in the specified timeframe. 

*	The survey response rate - the percentage of participants sampled who returned the survey. 

*	HCAHPS summary of Star Ratings - calculated using mean scores for each HCAHPS measure which was then categorized into a rating of 1, 2, 3, 4, or 5 using a statistical clustering algorithm. All measures are eligible to receive a star rating. Hospitals with fewer than 100 completed HCAHPS surveys within the current reporting period are not eligible to receive star ratings.

This report also includes state and national averages for each measure. These data may be useful in understanding how your hospital’s performance com- pares to other hospitals. The data for state and national values in this report only include CAHs with a signed MBQIP Memorandum of Understanding (MOU). The data used for this report are reported to the Centers for Medicare and Medicaid Services (CMS) and extracted from QualityNet.
CMS requires that CAHs submit ten months of data (reporting in all four quarters) to be considered reporting. In order for scores to be calculated for a quarter, CAHs must also have two or more completed surveys.

Specific information on how data elements were calculated for inclusion in this report is outlined below. Please direct questions regarding your MBQIP data reports to the Flex Coordinator in your state. You can find contact information for your Flex Coordinator at: https://www.ruralcenter.org/resources/state-flex-programs

**Measure Adjustment & Aggregation**
For each measure (composite or individual question), your hospital has a reported “adjusted score”, where data has been adjusted by CMS for the mix of patients and the mode by which the survey was administered. Adjusted scores show the percentage of survey respondents who selected certain responses to the survey questions, and is completed to reduce the bias in comparisons between hospitals. State measures aggregate all CAHs in the state and national measures aggregate all CAHs nationwide (not all hospitals nationwide). Values for state and national data may not always add to 100% due to rounding.

**Response Categories**

Response categories vary by question. For example, some questions use “Yes” or “No” as response options, where others have scales ranging from “Never” to “Always” or “Strongly Disagree” to “Strongly Agree”. For this report, some responses are combined into one category, for example “Sometimes to Never,” compared to “Usually” or “Always”.

**Benchmarks**

Benchmarks for the HCAHPS measures come from the benchmarks selected for CMS’ Hospital Value-Based Purchasing Program in 2023. HCAHPS Question 19 (patient recommendation) does not have a benchmark as part of these standards, and HCAHPS questions 8 and 9 (quietness and cleanliness) receive a joint benchmark.

**Data Exceptions & Labels**

*	“DNR” indicates that a CAH did not report data in at least 10 of the 12 months for the current reporting period.
*	“*” indicates that the CAH did not have eligible patients to survey or enough data to meet CMS criteria for analyses.
*	“N/C” indicates that less than 100 surveys were returned in the reporting period so a Star Rating was not able to be calculated. 
* “#” indicates that the CAH did not have a signed MOU at the time of reporting for this period.

